Title of the Master Thesis

### 2016-02-15 Master Thesis/synopsis.tex
Fix typo

\begin{definition}\label{5.1}
An abelian group is called \textit{free-by-finite} if its torsion subgroup $A_\text{tor}$ is finite and the quotien $A/A_\text{tor}$ is free abelian. $A$ is free-by-finite if and only if $A$ is the direct sum of a finite group and a free abelian group.
\end{definition}

\begin{lemma}\phantomsection\label{5.2}
\begin{enumerate}[(i)]
\item Let $A\to B$ be a homomorphism of abelian groups with finite kernel and cokernel. Then $A$ is free-by-finite iff $B$ is free-by-finite.
\item Let $0\to A'\stackrel{i}{\to}A\stackrel{p}{\to}A''\to 0$ be an exact sequence of abelian groups. If $A'$ and $A''$ are free-by-finite, then $A$ is free-by-finite. Conversely, if $A$ is free-by-finite, then $A'$ is free-by-finite. If additionally, $A'$ is finitely generated, then $A''$ is free-by-finite.
\item Let $A$ be free-by-finite. Then $\bigcap_{n\in\mathbb{N}}nA=0$.
\end{enumerate}
\end{lemma}

>>>>

\begin{definition}\label{5.1}
An abelian group is called \textit{free-by-finite} if its torsion subgroup $A_\text{tor}$ is finite and the quotient $A/A_\text{tor}$ is free abelian. $A$ is free-by-finite if and only if $A$ is the direct sum of a finite group and a free abelian group.
\end{definition}

\begin{lemma}\phantomsection\label{5.2}
\begin{enumerate}[(i)]
\item Let $f: A\to B$ be a homomorphism of abelian groups with finite kernel and cokernel. Then $A$ is free-by-finite iff $B$ is free-by-finite.
\item Let $0\to A'\stackrel{i}{\to}A\stackrel{p}{\to}A''\to 0$ be an exact sequence of abelian groups. If $A'$ and $A''$ are free-by-finite, then $A$ is free-by-finite. Conversely, if $A$ is free-by-finite, then $A'$ is free-by-finite. If additionally, $A'$ is finitely generated, then $A''$ is free-by-finite.
\item Let $A$ be free-by-finite. Then $\bigcap_{n\in\mathbb{N}}nA=0$.
\end{enumerate}
\end{lemma}
